---
title: "Report"
author: "SOFIN WADHWANIYA"
date: "27/10/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```  

# __Logistic regression__  


## ___Report of your Regression Model___  


### About Logistic Regression  


Logistic Regression, also known as Logit Regression or Logit Model, 
is a mathematical model used in statistics to estimate (guess) the 
probability of an event occurring having been given some previous data. 
Logistic Regression works with binary data, where either the event happens
(1) or the event does not happen (0).  


Like all regression analyses, the logistic regression is a predictive analysis.
Logistic regression is used to describe data and to explain the relationship 
between one dependent binary variable and one or more nominal, ordinal, interval
or ratio-level independent variables.  


Here, the response variables can be categorical or continuous, as the model 
does not strictly require continuous data. To predict group membership, logistic
regression uses the log odds ratio rather than probabilities and an iterative
maximum likelihood method rather than a least squares to fit the final model.
This means the researcher has more freedom when using logistic regression and the method may 
be more appropriate for non-normally distributed data or when the samples 
have unequal co-variance matrices.  


Thus, Logistic regression models the probabilities for classification 
problems with two possible outcomes. It's an extension of the linear
regression model for classification problems.  


### Overview of Data  


```{r}
library(DT)
library(shiny)
library(shinythemes)
library(summarytools)
library(ggplot2)
library(GGally)
library(Amelia)
library(ROCR)
library(pscl)
library(caret)
library(tidyverse)
library(rmarkdown)
df <- reactive(read.csv(input$dataset$datapath, header = input$header))
dtf <- reactive(subset(df(), select = c(input$columns,input$ind_columns)))
dtf2 <- reactive(na.omit(dtf()))
dtf3 <- reactive(subset(dtf2(), select = c(input$ind_columns)))
td <- reactive(read.csv(input$testdata$datapath))
td2 <- reactive(na.omit(td()))
head(dtf2())
```  


### Summary of Data  


```{r}
dfSummary(dtf2())
```  


### Structure of Data  


```{r}
str(dtf2())
```  


### Descriptive Statistics  


```{r}
descr(dtf2())
```  


### Pair Plot as Visualisation  


```{r}
ggpairs(dtf2(),aes(colour=as.factor(dtf2()[,input$columns])))
```  


### Regression  


#### Model Summary  


```{r}
model <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
summary(model)
```  


#### Coefficients  


```{r}
model3 <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
model3
```  


#### ANOVA Table  


```{r}
model2 <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
anova(model2, test="Chisq")
```  


### Model Assessment on your Test data  


#### Confusion Matrix  


```{r}
model5 <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
predicted_result <- predict(model5,newdata=td2(),type='response')
predicted_result2 <- ifelse(predicted_result > 0.5,1,0)
confusionMatrix(data=as.factor(predicted_result2), reference=as.factor(td2()[,input$columns]))
```  


### Prediction  


```{r}
pre_inp <- reactive(as.numeric(strsplit(input$predict,",")[[1]]))
pre_inp   # Your input values for prediction
temp <- dtf3()[1,]
temp[1,] <- pre_inp()
pd <- reactive(temp)
model6 <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
predicted_results <- predict(model6,newdata = pd(),type='response')
predicted_results2 <- ifelse(predicted_results > 0.5,1,0)
predicted_results2[1]   # Predicted Value
```  


### Performance Instance Plot (True vs False Positive Rate)  


```{r}
model4 <- glm(dtf2()[,input$columns] ~ ., family=binomial(link = "logit"), data=dtf3())
p <- predict(model4, newdata=td2(), type="response")
pr <- prediction(p, td2()[,input$columns])
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf)
```  


### Contact Details  


Name: Sofin Wadhwaniya"  


Email address: sofinwadhwaniya@gmail.com  





